### 2020-11-07 05_Thesis/THESIS_LaTeX/Chapters/1.tex
able to fit lin

Carbon nano-materials are subjected to great interest for research purposes due to their various potential applications in diverse areas that take advantage of the nano-scale properties. Carbon nano-materials are suitable for catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing, and cancer detection. Some matchless properties that allow carbon nano-materials to be utilized within multiple functionalities include high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties, and high conductivity. \cite{Siddiqui2019, McCreery2008, Geim2011, Zhu2010, Katsnelson2008, Li2008, Geim2007, Geim2009}

@@

Carbon is a versatile element capable to form a number of bonds with other elements or with itself. Furthermore, carbon orbitals have the ability to hybridize in sp1, sp2 and sp3 configurations, hence the existence of different types of allotropes, see Figure \ref{fig:carbonAllotropes}. Currently, the three carbon allotropes (diamond, amorphous carbon and graphite), have been joined by additional ones deriving from synthetic processes (such as graphene, carbon nano-tubes, fullerenes, carbon nanohorns, nanodiamonds) [ [12]; Fig. 1].

The interest in CBNs has increased exponentially in the last
decades, first with the discovery offullerenes (1985), then with that of carbon nanotubes (CNTs; 1991) and finally with the synthesis of graphene (GR) (2004).

\begin{figure}[th]
\centering
\includegraphics[width=1.0\textwidth]{./Figures/carbonAllotropes.png}
\decoRule
\caption[Carbon Allotropes]{Three carbon allotropes (diamond, carbyne and graphene) are the building blocks of additional deriving carbon types such as fullerenes, porous carbon and glass-like carbon.}
\label{fig:carbonAllotropes}
\end{figure}

The properties of these CBNs make them widely used in many
fields ranging from material science [13], energy production and storage [14], environmental sciences [15,16], biology [17-19] and medicine [20,21]. Table 1 summarizes the main properties of the most common CBNs [22-25]:

>>>>

Carbon nano-materials are subjected to great interest for research purposes due to their various potential applications in diverse areas that take advantage of the nano-scale properties. Carbon nano-materials are suitable for catalysis, adsorption, carbon capture, energy and hydrogen storage, drug delivery, bio-sensing, and cancer detection. Some matchless properties that allow carbon nano-materials to be utilized within multiple functionalities include high porosity, distinguished structures, uniform morphologies, high stability, high magnetic properties, and high conductivity. \cite{McCreery2008, Geim2011, Zhu2010, Katsnelson2008, Li2008, Geim2007, Geim2009, Siddiqui2019}

@@

\begin{figure}[th]
\centering
\includegraphics[scale=0.40]{./Figures/CBNfingerprint.png}
\decoRule
\caption[CBN Fingerprint]{Molecular to mesoscale structural features of synthetic polymers influence the emergence of specific microstructural features in polymer-derived carbon materials after pyrolysis.}
\label{fig:CBNfingerprint}
\end{figure}

Carbon is a versatile element capable to form a number of bonds with other elements or with itself. Cabon-based nano-materials (CBNs) exist in diverse forms, depending on the precise values of each degree of freedom that specify the material proclivity at multiple scales. Hybridization, crystallization, percolation, anisotropy, porosity, impurities and imperfections are some of the relevant features that determine the CBN set of properties. The combination of these features at the micro- and meso-scale burst a variety of macro-scale properties that comprise the CBN fingerprint (\ref{fig:CBNfingerprint}). The interminable collection of possible CBN fingerprints range from soft, conductive lubricants to very hard, low conductivity solids; and from black colour, bulks to transparent, disordered thin films. \cite{McCreery2008} Figure \ref{fig:carbonAllotropes} shows the existence of different types of allotrope as carbon orbitals have the ability to hybridize in sp1, sp2 and sp3 configurations, assembling different types of allotropes.

\begin{figure}[th]
\centering
\includegraphics[scale=0.40]{./Figures/carbonAllotropes.png}
\decoRule
\caption[Carbon Allotropes]{Three carbon allotropes (diamond, carbyne and graphene) are the building blocks of additional deriving carbon types such as fullerenes, porous carbon and glass-like carbon.}
\label{fig:carbonAllotropes}
\end{figure}

Due to the versatility and variety of CBNs, CBNs have been fabricated and implemented for various purposes. \cite{Geim2011, Katsnelson2008, Li2008, Geim2007, Geim2009, Siddiqui2019}. For instance, field effect transistors (FET) have been studied by Novoselov \cite{Novoselov2004} and Heersche et. al. \cite{Heersche2007}. Carbon FET devices have reported field-effect mobility one order of magnitude higher than that of silicon FETs. Other literature suggests CBNs to be favourable to detect a variety of gases and biomolecules. \cite{} As molecules are absorbed by the CBN, the carrier density and electrical resistivity of the carbon material changes.

%% Zhu2010

The properties of these CBNs make them widely used in many
fields ranging from material science [13, McCreery2008], energy production and storage [14], environmental sciences [15,16], biology [17-19] and medicine [20,21]. Table 1 summarizes the main properties of the most common CBNs [22-25]:

### 2020-11-07 05_Thesis/THESIS_LaTeX/Chapters/4.tex
able to fit lin

\chapter{Fabrication of Polymeric Fibers through Near-Field Electrospinning, and Forward-thinking on Photopolymerization and Pyrolysis} % Main chapter title

@@

>>>>

\chapter{Fabrication and Characterization of Polymeric Fibers through Near-Field Electrospinning, and Forward-thinking on Photopolymerization and Pyrolysis} % Main chapter title

@@

%----------------------------------------------------------------------------------------
%	SECTION 3
%----------------------------------------------------------------------------------------
\section{Comparison of the Obtained Polymer Fibres Against SU8-based Carbon Fibres and Potential Applications}
% Were the selected candidates electrospunable?
% Fiber morphology

### 2020-11-07 05_Thesis/THESIS_LaTeX/main.tex
able to fit lin

% Use the bibtex backend with the authoryear citation style (which resembles APA)
\usepackage[backend=biber,natbib=true]{biblatex}
% MLA, APA, or IEEE? - https://www.overleaf.com/learn/latex/Biblatex_citation_styles
%\usepackage[style=apa, backend=biber]{biblatex}

>>>>

% Import references handler
\usepackage[
    style     = ieee,         % references format style
    backend   = biber,        % choose the processing program
    natbib    = true,         % enable additional reference formats
    citestyle = numeric-comp, % enable multiple citations
    sortcites = true,         % sort references in multiple citations
    sorting   = none          % sort the reference table
]{biblatex}

### 2020-11-07 05_Thesis/thesis_proposal_LaTeX/Chapters/1_Introduction.tex
able to fit lin

\begin{figure}[th]
\centering
\includegraphics[width=0.95\textwidth]{./Figures/FabricationProcess.png}
\decoRule
\caption[Fabrication Process]{Fabrication process of carbon nano-wires to achieve through the proposed dissertation.}
\label{fig:fabricationFlowChart}
\end{figure}

Nanotechnology has explored different polymer patterning techniques to integrate carbon nano-wires structures. One technique is known as far-field electrospinning, a process in which electrified jets of polymer solution are dispensed to synthesize nano-fibers which then are pyrolyzed at high temperatures. One sub-technique derived from electrospinning is near field electromechanical spinning or EMS. EMS has proved to deliver high control in patterning polymeric nano-fibers. \cite{Cardenas2017}

The proposal is to continue the previous work done in regards to the synthesis of carbon nano-wires. Previous work includes the fabrication of suspended carbon nano-wires by two methods: electro-mechanical spinning and multiple-photon polymerization with a photoresist. \cite{Cardenas2017} This research proposal is intended to focus on electro-mechanical spinning processes only, to bring off polymer solutions that can be electrospun by near field electrospinning (NFES), photopolymerized and pyrolyzed into conducting carbon nano-wires. The polymer solutions described in \cite{Cardenas2017} are to be amended to achieve the goal mentioned in the previous statement.

Traditional near-field electrospinning or NFES allows large scale manufacturability combined with controlled guidance. \cite{Madou2011} However, the reported efforts required the use of electric fields in excess of 200 kV/m for continuous operation, resulting in limited control for nano-fiber patterning in traditional NFES processes. \cite{Madou2011} the current state-of-the-art synthesis processes for polymer nano-fibers lack to yield precise, inexpensive, fast, and continuous manufacturing properties.

>>>>

\begin{figure}[th]
\centering
\includegraphics[width=0.95\textwidth]{./Figures/FabricationProcess.png}
\decoRule
\caption[Fabrication Process]{Fabrication process of conductive carbon nano-wires to achieve through the proposed dissertation.}
\label{fig:fabricationFlowChart}
\end{figure}

Nanotechnology has led to the study of different polymer patterning techniques to integrate carbon nano-wires structures. One technique is known as far-field electrospinning, a process in which electrified jets of polymer solution are dispensed to synthesize nano-fibers which are then pyrolyzed at high temperatures. One sub-technique derived from electrospinning is near field electromechanical spinning or EMS. EMS has proved to deliver high control in patterning polymeric nano-fibers. \cite{Cardenas2017}

The proposal is to continue the previous work done in regards to the synthesis of carbon nano-wires. Previous work includes the fabrication of suspended carbon nano-wires by two methods: electro-mechanical spinning and multiple-photon polymerization with a photoresist. \cite{Cardenas2017} This research proposal is intended to focus on electro-mechanical spinning processes only, to bring off polymer solutions that can be electrospun by near field electrospinning (NFES), photopolymerized and pyrolyzed into conducting carbon nano-wires. The polymer solutions described by Cardenas \cite{Cardenas2017} are to be amended to achieve the goal mentioned in the previous statement.

Traditional near-field electrospinning or NFES allows large scale manufacturability combined with spatial control of material deposition. \cite{Madou2011} However, the reported efforts required the use of electric fields in excess of 200 kV/m for continuous operation, resulting in limited control for nano-fiber patterning in traditional NFES processes. Madou et al. \cite{Madou2011} conclude that the current state-of-the-art synthesis processes for polymer nano-fibers lack to yield precise, inexpensive, fast, and continuous manufacturing properties.
